Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for Collaborative Interactive Learning Techniques

### 2018-08-11 paper.tex
Add recommendations from reviews

\documentclass[conference,compsoc]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

@@

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

@@

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Resolving Limits Faced by Classical Machine Learning Approaches:\\Areas of Application for 
Collaborative Interactive Learning Techniques}

@@

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page (and note that there is less available width in this regard for
% compsoc conferences compared to traditional conferences), use this
% alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning (ML)} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18Th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{automatic ML (aML)}. In this ML paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a systems whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical ML approaches 
in comparison with CIL and outlines possible areas of application. 
\notes{Abstract kuerzen, 18th Jahrhundert interessiert niemanden.}
\end{abstract}

\section{Introduction}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a Computer Scientist from Carnegie Mellon University, ML tries 
to answer how we can build algorithms that automatically improve through 
experience and what fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
the Internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, we can see the 
results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell}, 
not limited to the list below.
\begin{itemize}
    \item \textit{Text classification, Natural Language Processing (NLP)}. 
        Many current mail programs have built-in spam detection which originally used
        simple regular expressions in order to detect phrases commonly used in spam mails.
        With state-of-the-art ML techniques it is not only possible for a mail program to 
        query for a number of words but to the pattern how spam mails are constructed and 
        to adapt itself to new types of spam.
    \item \textit{Speech recognition}. 
        Most commercial applications for speech recognition use ML to train itself to 
        recognize a users speech input. \notes{Umformen. Beschreiben, wofür ML genutzt wird.}
    \item \textit{Image recognition, OCR}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifiying 
        objects or recognize handwritten \notes{only handwritten?} characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses. 
        \notes{Nochmal eine Quellenangabe?}
    \item \textit{Games}.
        Computer Games ususally offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a realtively small game tree conatining 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily be computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents modern Games are using ML to gain experience 
        by themselves.
    \item \textit{Search engines, Recommendation systems}.
        Nearly all current search machines use ML in one fashion or another. They mainly use these 
        techniques for \textit{(1) User classification}\notes{[q?]} in order to offer personalized 
        search results and for \textit{(2) Query classification} in order to ``understand' a 
        users query and to provide further meaningful information.
\end{itemize}

Despite the successfull application of ML in a lot of fields, most of these examples 
need a sufficient amount of labeled training data ($x_i$ with assigned $y_i$) in order to make 
correct predictions on or discover structured patterns in unknown data $x_j$. However, most 
data sets in the biomedical domain, in robotics or in other fields, where data is collected 
from sensor systems or other unreliable sources, are often either not available (e.g.\ rare 
diseases, borderline cases in road traffic, \dots) or contain noisy data, dirty data or unwanted 
data due to dirty sensors or poor visibility conditions in camera applications.
In addition, a machine learning algorithms prediction is solely based on the training data it 
has seen before. One might argue, that human decisions are also only based on experience they have 
made since their childhood but humans are often still superior to most algorithms in terms of 
the instinctive interpretation of complex patterns. Furthermore, they can learn to recognize 
structural patterns from very few training data.

@@

This article gives a brief introduction on possible areas of application for the CIL-approach. 
It starts with an overview of classical machine learning scenarios, discussing where they are 
facing limits and motivating the use of CIL\@. It then lists possble applications and concludes 
with a view on future research interests.\notes{Relation to Organic Computing?}

\section{Algorithmic Foundations}
Before we take a closer look at the applications and challenges of CIL, first consider the 
following existing machine learning strategies and algorithms. As already mentioned above, 
there is a multitude of definitions for the term ML\@. But primarily, Arthur Samuel 
coined this term in 1959. Of course, a lot has changed in this area since then, 
however, the definition that ML allows computers to solve problems without being 
specifically programmed to do so, is still valid today\cite{MLStudiesUsingCheckers:samuel}.

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
In the following section we want to present five strategies\cite{FoundationsOfML:mohri}.

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and used in a variety of applications 
where labeled data is easy to obtain. The spam mail example discussed in the introduction is an 
instance of supervised learning.

\subsection{Unsupervised learning}
In contrast to supervised learning, with this technique the learner only receives 
unlabeled training data and makes predictions for all unseen points. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups\cite{BrainInf:holzinger}.

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabelled data and makes predictions for all unseen points.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is expensive.

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@. 
The learner interacts with his environment to gain new information. For each action 
he'll gets a reward. His goal is to maximize his reward over several repetitions. 
However, he is in conflict with using what has already been won by his actions 
or to get more information through further actions.

\subsection{Active Learning}\label{active}
The goal of Active Learning is to interact with other agents in a clever way in order 
to label already existing data points and thus achieve a similar performance at less available 
Information as in the method of supervised learning. To achieve this, 
the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
an action has enough information content to label a data point or not.

\section{When is using CIL helpful?}\label{AdvantageOfCIL}
In established ML systems, a separate model must be developed and trained in advance for 
each specific application. ML systems therefore have a relatively narrow application frame. 
The idea behind CIL systems is that they learn and self-organize knowledge throughout their lives. 
They collect information from various sources and evaluate the obtained data, so that they 
can solve problems together with other technical and human agents in a 
collaborative and interchangeable way\cite{CIL:sick}.
The CIL approach therefore deliberately integrates other intelligent systems 
(people and machines) into the decision-making process in order to ensure that the individual entities 
can solve otherwise difficult problems much easier.
Another difference to classical approaches is the mutual benefit. 
Machines not only benefit from training data of other agents, but also provide 
an own contribution to actively support people's collaboration processes by 
recognising their wishes and needs and reacting accordingly\cite{CIL:sick}.
\notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}

\section{Classification of CIL in Organic Computing}
CIL systems can be understood as organically structured information technology
which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeckt}.
They
\begin{itemize}
    \item configure themselves in the sense that they are not aligned by developers to an application case,
    \item optimize themselves by applying various strategies of ML to expand their knowledge,
    \item heal and protect themselves because cooperation with other systems is possible.
\end{itemize}
Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
during development\cite{Organic:schloer}.

\section{Application examples}
\subsection{Clustering}
Clustering is the perfect example of a starting point without sufficient information about a database. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure.
Clustering is used, for example, in most recommendation systems of popular Internet applications (Netflix movie recommendations, YouTube Video Tags \notes{[?]}) to group similar tags or find groups of people with a similar taste in movies.
Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified.

Unfortunately, real-world data in these areas is often unclean, contains false or unwanted data and is often present in 
dimensions $>$3, so that people alone, who are otherwise very good at recognizing similarities, are dependent on ML and vice-versa.

There are different approaches to cluster data into homogeneous groups. One of them is the k-Means algorithm\notes{[?]}. This requires at the beginning the number of $k$ clusters it should find. It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid. After the assignment, each centroid is placed at the center of all items assigned to it. This process of assigning the items and moving the centroids to
the center is now repeated until the assignments of the items no longer change.

What all cluster algorithms have in common is that they need a way to compare data points for similarity.
Classically, data points are tried to display in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
similarity, when a small result means more similar, is defined as
\begin{equation}
    similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
\end{equation}

Since data is usually multidimensional, i.e.\ much larger than three, suitable attributes must be selected for the comparison. 
However, the problem here is that similarity functions are influenced by subjective factors, since experts from different 
fields also find different partial aspects of the amount of data to be investigated interesting.
Therefore, the CIL approach can provide a decisive advantage in this case, as the knowledge and assessment of 
different experts and other systems can be used to make such decisions.
An interesting interactive approach follows\notes{[1]} to create a personal gazetteer from a users location data.

\subsection{Health Domain}

\subsection{Industry and Manufacturing}

\subsection{Agriculture}

\section{Challenges and future directions}
Challenges
Ethical Questions

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

>>>>

\documentclass[conference]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

@@

@@

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

@@

@@

\begin{document}
\title{Resolving Limits Faced by Classical Machine Learning Approaches: Areas of Application for 
Collaborative Interactive Learning Techniques}

@@

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning (ML)} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{automatic ML (aML)}. In this ML paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a system's whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical ML approaches 
in comparison with CIL and outlines possible areas of application. 
\end{abstract}

\section{Introduction}\label{sec:intro}
\notes{[Introduce abbreviations again.]}
\notes{[Introduction is too long, the examples shouldn't be in the introduction in detail.--> extra section]}
As with most concepts, there is no canonical 
definition for the term \textit{Machine Learning} but at its most basic form it 
can be described as algorithms that learn from a given set of training examples 
$\{(x_i, y_i)\}$ of inputs $x_i$ and outputs $y_i$ in order to 
make predictions on unknown input data. According to Tom 
Mitchell, a computer scientist from Carnegie Mellon University,  ML tries 
to answer how we can build algorithms that automatically improve through 
experience and which fundamental laws govern all these learning processes\cite{ML:mitchell}.
The area of ML in general is a fast-growing discipline at the intersection of statistics 
and computer science and has experienced massive research interest in the last decades.
With its various application possibilities it has also been an interesting branch for 
economists and entrepreneurs.
Since ML scenarios like \textit{supervised}, \textit{unsupervised} and 
\textit{semi-supervised} learning, which we will cover later, are heavily data-driven, 
the internet with its massive amount of data has contributed to the further development 
of research in the area of fully automated learning algorithms. Today, we can see the 
results in a variety of applications\cite{FoundationsOfML:mohri}\cite{DisciplineOfML:mitchell}, 
not limited to the list below.
\begin{itemize}
    \item \textit{Text classification, Natural Language Processing (NLP)}. 
        Many current mail programs have built-in spam detection which originally used
        simple regular expressions in order to detect phrases commonly used in spam mails.
        With state-of-the-art ML techniques it is not only possible for a mail program to 
        query for a number of words but to recognise patterns of how spam mails are constructed and 
        to adapt itself to new types of spam.
    \item \textit{Speech recognition}. 
        Most commercial applications for speech recognition also use ML to train itself to 
        recognise a user's speech input in order to perform further semantic analysis on
        that data.
    \item \textit{Image recognition, OCR}.
        Machine Learning methods have also been successfully applied in domains where it's 
        important to extract information from images such as detecting and classifying 
        objects or recognizing handwritten characters. Image 
        recognition and OCR are therefore for example used in medical diagnosis to 
        detect cancer on radiographs, in autonomous vehicles to detect obstacles and to 
        stay on track or in post-offices to sort envelopes with hand-written addresses
        \cite{DisciplineOfML:mitchell}.
    \item \textit{Games}.
        Computer Games usually offer a Multiplayer mode where a user can interact and 
        play the game even without a human opponent. For games with a small number of 
        possible moves after each turn, and therefore a relatively small game tree containing 
        all possible moves, the minimax algorithm\cite{Prog2:bachmaier} can be sufficient. 
        It figures out which next move would minimize the worst-case scenario for all subsequent 
        moves. Therefore, it needs to know all possible moves, which can easily become computationally 
        infeasible for games like Chess or AlphaGo where a general move faces between 35 (Chess) and 
        250 (AlphaGo) possible subsequent game states.
        In order to still have challenging opponents, modern Games are using ML to gain experience 
        by themselves.
    \item \textit{Search engines, Recommendation systems}.
        Nearly all current search machines use ML in one fashion or another. They mainly use these 
        techniques for \textit{(1) User classification}\cite{DisciplineOfML:mitchell} in order to offer personalized 
        search results and for \textit{(2) Query classification} in order to ``understand' a 
        users query and to provide further meaningful information.
\end{itemize}

Despite the successful application of ML in a lot of fields, most of these examples 
need a sufficient amount of labeled training data ($x_i$ with assigned $y_i$) in order to make 
correct predictions on, or discover structured patterns in unknown data $x_j$. However, most 
data sets in the biomedical domain, in robotics or in other fields, where data is collected 
from sensor systems or other unreliable sources, often are either not available (e.g.\ rare 
diseases, borderline cases in road traffic, \dots) or contain noisy data, dirty data or unwanted 
data due to dirty sensors or poor visibility conditions in camera applications.
In addition, a machine learning algorithm's prediction is solely based on the training data it 
has seen before. One might argue that human decisions are also only based on experience having been
made since their childhood but humans are often still superior to most algorithms in terms of 
the instinctive interpretation of complex patterns. Furthermore, they can learn to recognize 
structural patterns from very few training data.

@@

This article gives a brief introduction on possible areas of application for the CIL-approach. 
It starts with an overview of classical machine learning scenarios, discussing where they are 
facing limits, describing the relation to Organic Computing and motivating the use of CIL\@. 
It then lists possible applications and concludes 
with a view on future research interests.

\section{Algorithmic Foundations}
Before we take a closer look at the applications and challenges of CIL, let's first consider the 
following existing machine learning strategies and algorithms. As already mentioned above, 
there is a multitude of definitions for the term ML\@. But primarily, Arthur Samuel 
coined this term in 1959. Of course, a lot has changed in this area since then, 
however, the definition that ML allows computers to solve problems without being 
specifically programmed to do so, is still valid today\cite{MLStudiesUsingCheckers:samuel}.

Over the last decades, ML has developed significantly and has become an area of
research interest for many different actors, which makes it difficult to divide learning 
strategies into several categories. Different researchers are using different approaches 
for that\cite{FoundationsOfML:mohri}\cite{Structure:corne}. 
In the following section I want to present five strategies\cite{FoundationsOfML:mohri}.
\notes{[Add examples for each classification.]}

\subsection{Supervised learning}
Basically supervised learning is the way of learning from labeled examples and making predictions 
for all unseen points. This is the most basic concept of ML and used in a variety of applications 
where labeled data is easy to obtain. The spam mail example discussed in the introduction is a 
case of supervised learning.

\subsection{Unsupervised learning}
In contrast to supervised learning, the learner here receives only 
unlabeled training data and makes predictions for all unseen points. This technique is 
relatively similar to the way infants learn new things (e.g.\ learning a language) and 
is used, for example, in clustering data into groups, which we will discuss later\cite{BrainInf:holzinger}.
\notes{[Maybe Clustering as an example.]}

\subsection{Semi-supervised learning}
As the name suggests, the learner receives training data, which consists of both 
labeled as well as unlabelled data and makes predictions for all unseen points.
This technique is mainly used in areas where data is easily accessible, 
but finding the right label is expensive.
\notes{[Example needed.]}

\subsection{Reinforcement Learning}\label{reinforcement}
Reinforcement learning is probably the oldest approach and a potentially important one for CIL\@.\notes{[why?]} 
The learner constantly interacts with its environment to gain new information. For each action 
he gets a reward. The goal of the learner is to maximize its reward over several repetitions. 
However, he is in conflict with using the information which has already been discovered by his actions 
or with getting more information through further actions.
\notes{[too short.]}

\subsection{Active Learning}\label{active}
The goal of Active Learning is to interact with other agents in a clever way in order 
to label already existing data points and thus achieve a similar performance at less available 
information as in the method of supervised learning. To achieve this, 
the learner needs a selection strategy\cite{ActiveToDedicated:calma} that decides whether 
an action has enough information content to label a data point or not.
\notes{[too short.]}

\section{When using CIL is helpful}\label{AdvantageOfCIL}
In established ML systems, a separate model must be developed and trained in advance for 
each specific application. ML systems therefore have a relatively narrow application frame. 
The idea behind CIL systems is that they learn, self-organize and improve knowledge throughout their lives. 
They collect information from various sources and evaluate the obtained data, so that they 
can solve problems together with other technical and human agents in a 
collaborative and interchangeable way\cite{CIL:sick}.
The CIL approach therefore deliberately integrates other intelligent systems 
(people and machines) into the decision-making process in order to ensure that the individual entities 
can solve otherwise difficult problems much easier.
Another difference to classical approaches is the mutual benefit. 
Machines not only benefit from training data of other agents, but also provide 
an own contribution to actively support human collaboration processes by 
recognising their wishes and needs and reacting accordingly\cite{CIL:sick}.

\section{Classification of CIL in Organic Computing}
\notes{[The author could introduce the domain of Organic Computing a little more in detail, e.g.\ by describing the self-x properties.]}
CIL systems can be understood as organically structured information technology
which fulfill so-called self-x-properties\cite{Organic:schloer}\cite{Organic:schmeck}.
They
\begin{itemize}
    \item configure themselves in the sense that they are not aligned by developers to an application case,
    \item optimize themselves by applying various strategies of ML to expand their knowledge,
    \item heal and protect themselves because cooperation with other systems is possible and desired.
\end{itemize}
Depending on which methods of ML are used, CIL systems are also more or less self-explanatory 
during development\cite{Organic:schloer}.
\notes{[why?]}

\section{Application examples}
In the following we will discuss some interesting application examples.

\subsection{Clustering}
\notes{[Clustering is not really a domain on it's own but can be used to solve problems in health domain, etc.\ pp.]}
\notes{[Clarify the k-Means Algorithm by pointing out the steps.]}
Clustering is the perfect example of a starting point without sufficient information about an amount of data. 
The basic goal here is to divide a data set into homogeneous groups of individual data points in order to create structure in it.
In this context data points must be checked for similarity in some way.
Clustering is used, for example, in most recommendation systems of popular internet applications (Netflix movie recommendations, YouTube Video Tags\cite{YouTube:pasca}) to group similar tags or find groups of people with a similar taste in movies.
Furthermore, clustering is used to identify communities in social networks, for example for target-advertising, or to cluster location-data so that "important places" of a person can be identified\cite{DJ:frankowski}.

Unfortunately, real-world data in these areas is often unclean, contains false or unwanted data and is often present in 
dimensions $>$3, so that people alone, who are otherwise very good at recognizing similarities in dimensions $\le3$, are dependent on ML and vice-versa.

There are different approaches to cluster data into homogeneous groups. One of them is the k-Means algorithm\cite{FoundationsOfML:mohri}. In the beginning it requires the number of $k$ clusters it is supposed to find. 
It then randomly places $k$ centroids in space, which should represent the center of a cluster, and assigns each item to the nearest centroid. After the assignment, each centroid is placed at the center of all items assigned to it. This process of assigning the items and moving the centroids to
the center is now repeated until the assignments of the items no longer change.

What all cluster algorithms have in common is that they need a way to compare data points for similarity respectively distance.
Classically, data points are tried to be displayed in an n-dimensional metric space and, for example, their Euclidean distance is measured for similarity.
The Euclidean distance between two data points $p = (p_1, p_2, \dots, p_n)$ and $q = (q_1, q_2, \dots, q_n)$ and thus their
similarity, when a small result means more similar, is defined as
\begin{equation*}
    similarity(p, q) = \sqrt{\sum_{i=1}^{n} (q_i - p_i)^{2}}.
\end{equation*}

Since data is usually multidimensional, i.e.\ much larger than three, suitable attributes must be selected for the comparison. 
However, the problem here is that similarity functions are influenced by subjective factors, since experts from different 
fields also find different partial aspects of the amount of data that is examined interesting.
Therefore, the CIL approach can provide a decisive advantage in this case, as the knowledge and assessment of 
different experts and other systems can be used to make such decisions.
An interesting interactive approach follows\cite{DJ:frankowski}, which creates a personal gazetteer from a user's location data 
by interactively asking the right questions after cleaning the data from unwanted noise.

\subsection{Health Domain}
Also and especially in medical diagnosis, doctors are often confronted with a very small amount of data.
For rare diseases in particular, there are not enough training examples to use classical ML approaches efficiently and with a low error rate in practice.
In many areas, such as emergency surgery, results are often required within a very short time, which makes pure ML techniques useless in a lot of cases.
After successfully completing their medical studies, however, doctors, even with relatively little experience, already have the ability to examine and classify X-rays sufficiently accurately for various diseases and anomalies.
In these cases the intuitiveness of one or more people can profitably support the CIL system.

Another area of application in the field of medical research also takes advantage of human puzzle-solving intuition. 
For years the project "foldit" of the University of Washington has achieved remarkable results\cite{Foldit:results} from the gamification of a problem related to biology.
The researchers have developed a game that helps them to optimize and predict possible protein structures with the help of 
players\cite{Foldit:web}.
Proteins can fold in a number of different ways. Even with smaller proteins, the number of possible folds can be extremely high due to their many degrees of freedom.
The aim of the game is to determine the optimal folding and thus the "most comfortable" state of a protein in order to be able to develop appropriate drugs for and with this shape.
Since the structure determines the function of a protein\cite{Foldit:web}, new forms can also be used to treat diseases such as AIDS or cancer more effectively.

So we already see a system in this field that at least involves the human being as a collective form of knowledge acquisition in the solution of complex problems, even if not directly with technical systems.
The next step towards CIL in this area could be to incorporate the results of human puzzle-solving into the calculations and decisions of ML systems in order to proactively support humans (bi-directional way of inputs, see section~\ref{sec:intro}) in finding solutions (for example by excluding unpromising folds).

\subsection{Industry and Manufacturing}
The primary goal in manufacturing is to keep production up and running under almost all circumstances. 
Even short downtimes of production lines result in high sales losses for companies.
This is why it is important to keep an eye on the wear of work equipment, production lines and the condition of machines in general at all times.
Current systems already use various ML techniques\cite{Manu:wuest} to cover these applications.

For CIL-systems, it is conceivable, in addition to the sensor data used by the devices to "measure" wear, to call in expert knowledge, so that rare cases that are easily recognisable as a suspicious situation for humans, can be identified at an early stage by the whole system.
In this process, a CIL system must estimate at runtime which expert should be asked what and when in order 
to achieve maximum information content.

\section{Challenges and future directions}
Since the area of Collaborative Interactive Learning is a very new field of research, there is still a lot of 
research to be done in the areas of continuous knowledge acquisition 
and evaluation from several heterogeneous sources (Internet, expert knowledge, etc.), 
as well as the interaction with multiple other agents (humans and other CIL systems), 
especially when systems have to adapt to changing situations during their lifetime.

Not only technical difficulties have to be overcome, but also social ones. In order to use ML techniques effectively, 
at least a minimum amount of data has to be provided in order to be analyzed. To do this, we need to decide 
to what extent we are willing to disclose our data for the benefits of CIL systems and ML in general.
Inhibitions in human-machine communication and interaction must also be overcome for CIL systems to be used 
successfully and productively.
